Resilience and Home-Space for WSTS

### 2024-01-11 diapo/presentation.tex
ip
up

%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Outline}

\tableofcontents
  \end{frame}
  \section{Introduction}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Motivation}

@@

   \begin{center}
 	\begin{figure}
 	\vspace{.06cm}
\includegraphics[width=.50\textwidth]{FigA}
	\end{figure}
\end{center}

@@

   \begin{center}
 	\begin{figure}
 	\vspace{.06cm}
\includegraphics[width=.50\textwidth]{FigA}
	\end{figure}
\end{center}

$\Safe = \{q_0(n) \mid n \in \N\}$

@@

$\Safe = \{q_1(0)\} $

@@

   \begin{center}
 	\begin{figure}
% 	\hspace{-2.cm}
\includegraphics[width=.50\textwidth]{FigB}
	\end{figure}
\end{center}

@@

  \begin{definition}[\cite{DBLP:journals/iandc/Finkel90}]
A {\em Well-Behaved Transition System} (WBTS) 
is a FAC\footnote{FAC = all anti-chains are finite}-ordered transition system $\mathscr{S}=(S, \rightarrow, \leq)$ such that   
%the transition relation $ \rightarrow$ is (upward) compatible with $\leq$, i.e., for all 
%$s_1, t_1 , s_2 \in S$
%	with $s_1 \leq s_2$  and $s_1 \rightarrow t_1$, there exists 
%	$t_2 \in S$ with 
%	$t_1 \leq t_2$ and $s_2 \rightarrow^{*} t_2$.
\end{definition}

@@

>>>>

%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
%  \begin{frame}{Outline}

%\tableofcontents
%  \end{frame}
  \section{Introduction}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Motivation}

@@

   \begin{center}
 	\begin{figure}
 	\vspace{.06cm}
\includegraphics[width=.47\textwidth]{FigA}
	\end{figure}
\end{center}

$\Safe = \{q_0(n) \mid n \in \N\}$, $\Bad$ complement of $\Safe$

\phantom{ {resilience},  {$k$-resilience} and {bounded resilience} are not satisfied }

$\Safe = \{q_1(0)\} $, $\Bad$ complement of $\Safe$

\phantom{ {resilience} hold, {bounded resilience} does not hold }

@@

   \begin{center}
 	\begin{figure}
 	\vspace{.06cm}
\includegraphics[width=.47\textwidth]{FigA}
	\end{figure}
\end{center}

$\Safe = \{q_0(n) \mid n \in \N\}$, $\Bad$ complement of $\Safe$

@@

$\Safe = \{q_1(0)\} $, $\Bad$ complement of $\Safe$

@@

   \begin{center}
 	\begin{figure}
% 	\hspace{-2.cm}
\includegraphics[width=.47\textwidth]{FigB}
	\end{figure}
\end{center}

@@

  \begin{definition}[\cite{DBLP:journals/iandc/Finkel90}]
A {\em Well-Behaved Transition System} (WBTS) 
is a FAC$^1$-ordered transition system $\mathscr{S}=(S, \rightarrow, \leq)$ such that   
%the transition relation $ \rightarrow$ is (upward) compatible with $\leq$, i.e., for all 
%$s_1, t_1 , s_2 \in S$
%	with $s_1 \leq s_2$  and $s_1 \rightarrow t_1$, there exists 
%	$t_2 \in S$ with 
%	$t_1 \leq t_2$ and $s_2 \rightarrow^{*} t_2$.
\end{definition}

@@

\phantom{line}

{\small $^1${FAC = all anti-chains are finite}}
